---
title: "EMU415 DBMS Homework1"
author: "team_yes_sql"
output:
  quarto::quarto_html:
    self_contained: true
    keep_md: true
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(DBI)
library(RMySQL)  
con <- dbConnect(MySQL(), host = "127.0.0.1", port = 3306, user = "root", dbname = "EMU415_yes_sql")
```

**TEAM MEMBERS**

```{r, message=FALSE, warning=FALSE}
# Retrieve and display team members' information
team_members <- dbGetQuery(con, "SELECT first_name, last_name, student_id FROM team_members")

print(team_members)

```

**QUESTION 5**

-    Find the total number of team members

```{sql connection= con}

SELECT COUNT(*) AS number_of_members FROM team_members;

```

-    List team members by age from oldest to youngest.

```{sql connection= con}

SELECT member_id, first_name, last_name, student_id, age FROM team_members ORDER BY age DESC;

```

-   Identify the range of expected graduation years within your team

    ```{sql connection= con}

    SELECT DISTINCT graduation_year FROM team_members;
    ```

-   Analyze the distribution of team members across different joining years

    ```{sql connection= con}

    SELECT COUNT(*) AS joined_2018 FROM team_members WHERE join_year = 2018;

    ```

    ```{sql connection= con}

    SELECT COUNT(*) AS joined_2019 FROM team_members WHERE join_year = 2019;

    ```

**QUESTION 6**

```{sql connection= con}

SELECT
    SHA1(CONCAT(
        COUNT(*),
        '-',
        MIN(graduation_year),
        '-',
        AVG(age)
    )) AS team_identifier
FROM
    team_members;

```

Cryptographic algorithms like SHA-1 are used in database management for various purposes, such as ensuring data integrity and security. For example, SHA-1 hashes can be computed for sensitive data like passwords before storing them in the database, making it difficult for attackers to recover the original passwords. Additionally, SHA-1 hashes can be used to verify the integrity of data stored in the database, ensuring that it has not been tampered with.
